---
title: "ROADEF"
author: "Franco Peschiera"
date: "February 14, 2018"
output: 
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
  beamer_presentation:
    incremental: yes
nocite: '@*'
bibliography: MFMP.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
```

## Introduction

## Problem

**Informally**:

Assign both missions and maintenance operations to a fleet of aircraft in order to maximize availability and minimize costs. Missions have particular needs in terms of aircraft and time.

## Example

<div style="font-size: 20px;">
```{r}
gantt
```
</div>

## Problem

**Formally**:

A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Since all tasks are already scheduled, we know time periods $T_j \subset \mathcal{T}$ in which they will be realized. Similarly, all the tasks to be realized in period $t$ are known and defined by set $J_t \subset \mathcal{J}$. 

Each task requires a certain number $r_{j}$ of resources $i \in \mathcal{I}$ which it employs for a time duration defined by $h_j$ in each period. Set $a_{j} \subset \mathcal{I}$ lists the resources that can be assigned to each task and set $O_i \subset \mathcal{J}$ consists of tasks for which resource $i$ can be used. The number of resources in use for each period $d_t$ is also known.

## Relevance and origin

The problem was born out of the need of the french Air Force to maximize the availability of their Mirage 2000 fleet.

In fact, a similar subject has been presented as a challenge in a open competition: Défit Opti-plan.

## State of the art

* In @Cho2011, US Army aircraft was assigned daily operations over a year to aircraft.
* In @Kozanidis2008, Greek aircraft had monthly assignments of maintenances and flight hours. 
* In @Verhoeff2015, monthly assignments were also done, and several objectives were taken into account: availability, serviceability and sustainability.
* In @Chastellux2017, a first version of the model was done, assigning missions instead of flight hours.

## State of the art (2)

The present model assigns missions to aircraft, permitting to add more complex functionality, such as minimum assignment durations.

This model also features several improvements in the MIP modelling that permit greater instance sizes.

## Model: sets

|Set|Description|
|-----|--------------------------------------------------------------------|
|    $\mathcal{T}_j$     |  time periods $t \in \mathcal{T}$ in which task $j$ is active. |
|    $\mathcal{J}_t$    |  tasks $j \in \mathcal{J}$ to be realized in period $t$. |
|    $\mathcal{I}_j$     |  resources $i \in \mathcal{I}$ that can be assigned to task $j$. |
|    $\mathcal{O}_i$     |  tasks $j \in \mathcal{J}$ for which resource $i$ can be used. |
|    $\mathcal{T}^{s}_t$ |  time periods $t' \in \mathcal{T}$ such that $t' \in \{ \max{\{1, t - M+1\}},  ..., {t}$\}. |

## Model: parameters

Only *main parameters* are shown

|Parameters|Description|
|--------------|-------------------------------------------------|
| $H_j$ |  amount of **resource time required** by task $j$. |
| $R_j$ |  number of **resources required** by task $j$. |
| $M$   |  **maintenance duration** in number of periods. |
| $E$   |  remaining **elapsed time** after a maintenance. |
| $H$   |  remaining **usage time** after a maintenance. |

<!-- ## Model: parameters (2) -->

<!-- |Parameters|Description| -->
<!-- |--------------|----------------------------------------------------------------------| -->
<!-- | $N_t$              | number of resources in already-planned maintenances in period $t$ at the beginning | of the planning ho |izon.| -->
<!-- | $D_t$              | number of resources to be assigned in total in period $t$. | -->
<!-- | $Rut^{Init}_{i}$   | remaining usage time for resource $i$ at the start of the planning horizon. | -->
<!-- | $Ret^{Init}_{i}$   | remaining elapsed time for resource $i$ at the start of the planning horizon. | -->
<!-- | $Ret^{Init}_{sum}$ | sum of remaining elapsed times at the start of the planning horizon. | -->
<!-- | $Rut^{Init}_{sum}$ | sum of remaining elapsed time at the start of the planning horizon. | -->

## Model: variables

| Variable   |  Description |
|-----------|------------------------------------------------------- |
| $a_{jti}$   |  =1 if **task** $j \in J$ in period $t \in \mathcal{T}_j$ **is realized with resource** $i \in \mathcal{I}_j$, 0 otherwise. |
| $m_{it}$    |  =1 if resource $i \in I$ **starts a maintenance** operation in period $t \in \mathcal{T}$, 0 otherwise. |
| $rut_{it}$  |  **remaining usage time** (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. |
| $ret_{it}$  |  **remaining elapsed time** (integer) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. |
| $u_{max}$   |  maximal number (integer) of **unavailable resources** in any period. |
| $m_{max}$   |  maximal number (integer) of **resources in maintenance** in any period. |

## Model: constraints (1)

$$
\begin{align}
&\sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq m_{max}
&t \in \mathcal{T} \\
&\sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t + D_t\leq u_{max} 
&t \in \mathcal{T}\\
&\sum_{i \in \mathcal{I}_j} a_{jti} = R_j
&j \in \mathcal{J}, t \in \mathcal{T}_j\\
&\sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
& t \in \mathcal{T}, i \in \mathcal{I}
\end{align}
$$

## Model: constraints (2)

Only usage time is shown. Elapsed times are treated in the same way.

$$
\begin{align}
& rut_{it} \leq rut_{it-1} + H m_{it} - \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j & t =1, ..., \mathcal{T}, i \in \mathcal{I}\\
& rut_{i0} = Rut^{Init}_i
        & i \in \mathcal{I}\\
& rut_{it} \geq H m_{it}
        & t \in \mathcal{T}, i \in \mathcal{I}\\ 
& rut_{it} \in [0,H]
        & t \in \mathcal{T}, i \in \mathcal{I} \\
& \sum_{i \in \mathcal{I}} rut_{it} \geq Rut^{Init}_{sum}
        & t = |\mathcal{T}|
\end{align}
$$


## Results


## Multi-objective

## Next steps

## References


